%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer internship}
    {Quantedge Capital}
    {Singapore}
    {May. 2023 - Aug. 2023}
    {
        \begin{cvitems}
            \item {Design, prototype and develop big data pipelines using Apache Spark and Delta Lake}
            \item {Improves local development process by streamlining local kubernetes and aws s3 setup}
            \item {Developed devops tools for integrating with databricks and achieved 0 cost local testing and 0 touch deployment through github actions and Terraform}
        \end{cvitems}
    }

  \cventry
    {Teaching assistant - CS2100}
    {National Univeristy Of Singapore}
    {Singapore}
    {Aug. 2022 - Nov. 2022}
    {
        \begin{cvitems}
            \item {Taught assembly, circuit design and cpu architecture during lab sessions}
        \end{cvitems}
    }

  \cventry
    {Software Engineer internship}
    {Alphalab Capital}
    {Singapore}
    {May. 2022 - Aug. 2022}
    {
        \begin{cvitems}
            \item {Fixed and resolved bugs in legacy python monolithic codebase while migrating legacy components to modern design}
            \item {Added arbitrage finding and trading capabilities by building trading infrastructure on ETH blockchain }
            \item {Improved trading account management by developing fullstack web tool for internal usage}
        \end{cvitems}
    }

  \cventry
    {Tools Developer internship} % Job title
    {STAR Labs} % Organization
    {Singapore} % Location
    {Nov. 2021 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on refactoring and profiled of a custom taint analysis tool written in angr}
      \end{cvitems}
    }

  \cventry
    {N-day Vulnerability Researcher internship} % Job title
    {STAR Labs} % Organization
    {Singapore} % Location
    {Mar. 2020 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Discovered and reported 3 vulnerabilities in Singtel Mesh Nodes, assigned CVE-2020-15357, CVE-2020-25545 and CVE-2020-25546.}
        \item {Reverse engineered and exploited VirtualBox display driver emulator.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}
